Exploring the Determinants of Body Weight: A Bayesian Analysis of Anthropometric and Demographic Factors Among Female U.S. Army Personnel

### 2024-12-11 paper/paper.qmd
Update paper.qmd
Improve Citation
Update paper.qmd
Check In-text Citations
Polishing Writing in Introduction Section

This paper is structured as follows: [@sec-data] describes the dataset and provides a descriptive analysis of the key variables. [@sec-model] explains the methodology, including the Bayesian regression model employed. [@sec-result] presents the findings, highlighting significant predictors and model performance. [@sec-discussion] discusses the implications, limitations, and future research directions. Lastly, [@sec-model-details] offers detailed posterior predictive checks, diagnostic plots, and their interpretations.

@@

The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S [@ANSURII_2012]. Army personnel, collected using standardized protocols to ensure accuracy. Unlike civilian datasets, it uniquely addresses the physical demands and characteristics of military personnel, offering valuable information on factors like fitness, injury risk, and gear design [@hotzman2011]. Its specificity makes it a vital resource for understanding and improving the health, safety, and operational readiness of female soldiers [@paquette2009].

@@

# Appendix {.unnumbered}

# Data Cleaning

@@

# Ideal Survey Methodology

>>>>

This paper is structured as follows: [@sec-data] describes the dataset and provides a descriptive analysis of the key variables. [@sec-model] explains the methodology, including the Bayesian regression model employed. [@sec-result] presents the findings, highlighting significant predictors and model performance. [@sec-discussion] discusses the implications, limitations, and future research directions. The appendix is divided into three sections: [Appendix -@sec-data-cleaning] discusses the data cleaning process, [Appendix -@sec-model-details] provides additional details of the modeling process, and [Appendix -@sec-ideal-survey] outlines an ideal survey methodology for improved data collection.

@@

The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S [@ansurII_2012]. Army personnel, collected using standardized protocols to ensure accuracy. Unlike civilian datasets, it uniquely addresses the physical demands and characteristics of military personnel, offering valuable information on factors like fitness, injury risk, and gear design [@hotzman2011]. Its specificity makes it a vital resource for understanding and improving the health, safety, and operational readiness of female soldiers [@paquette2009].

@@

# Appendix {-}

# Data Cleaning {#sec-data-cleaning}

@@

# Ideal Survey Methodology {#sec-ideal-survey}
